\documentclass[letterpaper,11pt]{article}
% packages used
	\usepackage{threeparttable}
	\usepackage[format=hang,font=normalsize,labelfont=bf]{caption}
	\usepackage{amsmath}
	\usepackage{array}
	\usepackage{delarray}
	\usepackage{amssymb}
	\usepackage{amsthm}
	\usepackage{natbib}
	\usepackage{caption}
	\usepackage{subcaption}
	\usepackage{setspace}
	\usepackage{float,color}
	\usepackage[pdftex]{graphicx}
	\usepackage{hyperref}
	\usepackage{multirow}
	\usepackage{tabularx}
	\usepackage{colortbl}
	\usepackage{float,graphicx,color}
	\usepackage{graphics}
	\usepackage{xcolor,colortbl}
	\usepackage{booktabs}
	\usepackage{tablefootnote}
	\usepackage{graphicx}
    \usepackage{placeins}
    \usepackage{authblk}
    \usepackage{caption}
% theorem settings
	\theoremstyle{definition}
	\newtheorem{theorem}{Theorem}
	\newtheorem{acknowledgment}[theorem]{Acknowledgment}
	\newtheorem{algorithm}[theorem]{Algorithm}
	\newtheorem{axiom}[theorem]{Axiom}
	\newtheorem{case}[theorem]{Case}
	\newtheorem{claim}[theorem]{Claim}
	\newtheorem{conclusion}[theorem]{Conclusion}
	\newtheorem{condition}[theorem]{Condition}
	\newtheorem{conjecture}[theorem]{Conjecture}
	\newtheorem{corollary}[theorem]{Corollary}
	\newtheorem{criterion}[theorem]{Criterion}
	\newtheorem{definition}{Definition} % Number definitions on their own
	\newtheorem{derivation}{Derivation} % Number derivations on their own
	\newtheorem{example}[theorem]{Example}
	\newtheorem{exercise}[theorem]{Exercise}
	\newtheorem{lemma}[theorem]{Lemma}
	\newtheorem{notation}[theorem]{Notation}
	\newtheorem{problem}[theorem]{Problem}
	\newtheorem{proposition}{Proposition} % Number propositions on their own
	\newtheorem{remark}[theorem]{Remark}
	\newtheorem{solution}[theorem]{Solution}
	\newtheorem{summary}[theorem]{Summary}
% other setup
	\hypersetup{colorlinks,linkcolor=red,urlcolor=blue,citecolor=red,hypertexnames=false}
	\graphicspath{{./figures/}}
	\DeclareMathOperator*{\Max}{Max}
	\bibliographystyle{aer}
	\numberwithin{equation}{section}
	\renewcommand\theenumi{\roman{enumi}}
	\newcommand\ve{\varepsilon}
	\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
	\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
	\newcommand{\TODO}[1]{ {\color{magenta} TODO: [#1]} }
	\newcommand\fnote[1]{\captionsetup{font=small}\caption*{#1}}
	\newcommand{\bftab}{\fontseries{b}\selectfont}


\begin{document}

\begin{spacing}{1.5}

\section{Model} \label{sec_Model}

	\subsection{Households}

		Bonds exist with maturities from 1 to $I$ periods into the future.  The price in period $t$ of a bond delivering 1 unit of real consumption in period $t+i$ is denoted $q_{it}$.  The quantity of bonds held in period $t$, coming due in period $t+i$ is denoted $b_{it}$.  Bonds are contracts structured so that the bond pays one unit of the final output good when the maturity goes to zero, i.e. $q_{it} = 1$.

		Households solve the following dynamic program:
		\begin{align}
			V(k_{t-1}, \{b_{i-1,t-1}\}_{i=1}^I; \Theta_t) & = \max_{x_t, \{b^{i,t+1}\}_{i=1}^I, l_t} [c_t^\gamma + \psi(1-l_t)^\gamma]^{\frac{\phi}{\gamma}} \nonumber \\
			& + \beta E \left\{ V(k_t, \{b_{it}\}_{i=1}^I; \Theta_{t+1}) \right\} \nonumber
		\end{align}
		\begin{align}
			\begin{split} c_t & = w_t l_t - \tau^l_t (w_t l_t - ded_t) + tr_t + r_t k_{t-1} + cr_t + \sum_{i=1}^I q_{it} b_{i-1,t-1} \\
			& - k_t - \sum_{i=1}^I  q_{it} b_{it} - x_t - \tau^k_t \left( r_t k_{t-1} - x_t\theta_t - A_t  \right) \end{split} \\
			A_t & \equiv \sum_{v=0}^\infty \delta_g (1-\delta_g)^v (1-\theta_{t-v}) \frac{P_{t-v} x_{t-v}}{P_t} \\
			k_t & = k_{t-1} (1-\delta) + e^{\omega_t} \left[ 1-S\left(\frac{x_t}{x_{t-1}} \right) \right] x_t 
		\end{align}
		
		where $\Theta_t$ is a set of variables known to the household.

		There is one Euler equation which implicitly defines $x_t$.

		There is another Euler equation which implicitly defines $l_t$.

		There are $I$ Euler equations which implicitly define the $\{b_{it}\}_{i=1}^I$.
		\begin{align}
			u_{c,t} q_{it} & = \beta E\left\{  u_{c,t+1} q_{i-1,b+1} \right\} \\
			u_{ct} & \equiv \phi [ c_t^\gamma + \psi(1-l_t)^\gamma]^{\frac{\phi-\gamma}{\gamma}} c_t^{\gamma-1} \label{eq_bEuler}
		\end{align}


	\subsection{Market Clearing}

		Markets for bonds of all maturities must clear each period.  Demand for bonds of maturity $i$ are denoted $b_{it}$ above.  Supply of bonds by the government will be denoted $B_{it}$.  Narket clearing gives:

		\begin{equation}
			b_{it} = B_{it}; \; \forall i, t
		\end{equation}
		
		The laws of motion for the supplies of bonds are as follows.  Each period the government issues a new set of assets of maturities 1 through $I$, we denote these as $B^N_{it}$  Assets of maturity 0 are retired.  This gives:
		\begin{align}
			B_{It} & = B^N_{It} \\
			B_{it} & = B_{i+1,t-1} + B^N_{it}; \text{ for } 1 \le i \le I-1
		\end{align}

		If the longest maturity is 6 periods and if the government only ever issues bonds of maturites 1 and 6, then we have $I=6$ and $B^N_{it} = 0$ if $1 < i < 6$.  The remaining $B^N_{1t}$ and $B^N_{6t}$ will follow some exogenous law of motion that refelcts government policy.

		Once we know the exogenous behavior of the supplies from above, the $I$ Euler equations from equation \eqref{eq_bEuler} now impliicty define the market clearing prices, $\{ q_{it} \}_{i=1}^I$, as functions of the state variables.  Hence, like $l_t$, bond prices are ``jump'' variables.

		The yield curve can be derived from the bond prices by calculating yield-to-maturity for simple bonds.
		\begin{align}
			q_{it} & = \left( \frac{1}{1+r_{it}} \right)^i \nonumber \\
			r_{it} & = q_{it}^{-\frac{1}{i}} - 1
		\end{align}
		

\end{spacing}

\end{document}